Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2015-09-03 paper.tex
Add CAD drawings of RVAT
Add subsubsections for 3D wake comparisons
Add note about tip loss corrections

    \caption{CAD model of the UNH-RVAT cross-flow turbine}

@@

@@

>>>>

    \includegraphics[clip, trim=0 1in 0 1in, width=0.8\textwidth]{figures/CAD}

    \caption{CAD drawings of the UNH-RVAT cross-flow turbine as designed (left)
        and cleaned for simulation (right).}

@@

\subsubsection{Mean velocity in three dimensions}

% In this section, show mean velocity contours/quivers

\subsubsection{Turbulence kinetic energy contours}

% Compare contours of TKE for 2 simulation cases and experiments

@@

These results may also help develop new tip loss corrections for blade element
type models, which currently only exist for axial-flow rotors.
